MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Model Selection

### 2020-04-14 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
comment out nonessential code for testing

# Add in RIN^2 values
COVARIATES$RIN2 = COVARIATES$RIN^2
ContCovariates = c(ContCovariates, 'RIN2')
```
Correlation/association between covariates at an FDR <= 0.1
```{r covariates.correlation, fig.width=10, fig.height=8}
COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 0.05)
tmp = COVARIATES.CORRELATION$ESTIMATE
tmp[COVARIATES.CORRELATION$PVAL > 0.05] = 0
h = Heatmap(tmp, col = colorRamp2(c(-1,0,1), c('blue','white','red')), name = 'AssocEstimate')
ComplexHeatmap::draw(h, heatmap_legend_side = 'left')
```

>>>>

# Add in RIN^2 values
COVARIATES$RIN2 = COVARIATES$RIN^2
ContCovariates = c(ContCovariates, 'RIN2')
```
<!-- Correlation/association between covariates at an FDR <= 0.1 -->
<!-- ```{r covariates.correlation, fig.width=10, fig.height=8} -->
<!-- COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 0.05) -->
<!-- tmp = COVARIATES.CORRELATION$ESTIMATE -->
<!-- tmp[COVARIATES.CORRELATION$PVAL > 0.05] = 0 -->
<!-- h = Heatmap(tmp, col = colorRamp2(c(-1,0,1), c('blue','white','red')), name = 'AssocEstimate') -->
<!-- ComplexHeatmap::draw(h, heatmap_legend_side = 'left') -->
<!-- ``` -->
